{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2016-12-15 sftrends_manu.Rnw
yaxis lab to flow comp plots

# ggplot theme
mythm <- theme_minimal() +
  theme(
    legend.position = 'top', 
    legend.title = element_blank(),
    axis.title.y = element_blank(),
    panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"), 
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  )

# year only
toplo1 <- filter(trnds_seasyr, cat %in% c('1976-1995', '1996-2013'))
p1 <- ggplot(toplo1, aes(x = tau, y = Site_Code)) + 
  geom_point(aes(pch = trnd, colour = abs(tau)), size = 4, alpha = 0.8) + 
  facet_grid(cat~resvar, labeller = label_parsed
    ) + 
  geom_vline(xintercept = 0, linetype = 'dashed') + 
  mythm + 
  xlab(expression(tau)) +
  scale_shape_manual(values = c(16, 1, 17, 2)) +
  scale_colour_gradient(low = 'grey60', high = 'black', guide = F) + 
  scale_x_continuous(limits = c(-1, 1)) + 
  geom_hline(yintercept = c(3.5, 6.5), colour = 'grey', alpha = 0.6)

# seasonal, first years
toplo2 <- filter(trnds_seasyr, !cat %in% c('1976-1995', '1996-2013')& ann == 'bef') 
p2 <- ggplot(toplo2, aes(x = tau, y = Site_Code)) + 
  geom_point(aes(pch = trnd, colour = abs(tau)), size = 4, alpha = 0.8) + 
  facet_grid(cat~resvar, labeller = label_parsed
    ) + 
  geom_vline(xintercept = 0, linetype = 'dashed') + 
  mythm + 
  xlab(expression(tau)) +
  scale_shape_manual(values = c(16, 1, 17, 2)) +
  scale_colour_gradient(low = 'grey60', high = 'black', guide = F) + 
  scale_x_continuous(limits = c(-1, 1)) + 
  geom_hline(yintercept = c(3.5, 6.5), colour = 'grey', alpha = 0.6)

# seasonal, first years
toplo3 <- filter(trnds_seasyr, !cat %in% c('1976-1995', '1996-2013')& ann == 'aft')
p3 <- ggplot(toplo3, aes(x = tau, y = Site_Code)) + 
  geom_point(aes(pch = trnd, colour = abs(tau)), size = 4, alpha = 0.8) + 
  facet_grid(cat~resvar, labeller = label_parsed
    ) + 
  geom_vline(xintercept = 0, linetype = 'dashed') + 
  mythm + 
  xlab(expression(tau)) +
  scale_shape_manual(values = c(16, 1, 17, 2)) +
  scale_colour_gradient(low = 'grey60', high = 'black', guide = F) + 
  scale_x_continuous(limits = c(-1, 1)) + 
  geom_hline(yintercept = c(3.5, 6.5), colour = 'grey', alpha = 0.6)

>>>>

# ggplot theme
mythm <- theme_minimal() +
  theme(
    legend.position = 'top', 
    legend.title = element_blank(),
    panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"), 
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  )

# year only
toplo1 <- filter(trnds_seasyr, cat %in% c('1976-1995', '1996-2013'))
p1 <- ggplot(toplo1, aes(x = tau, y = Site_Code)) + 
  geom_point(aes(pch = trnd, colour = abs(tau)), size = 4, alpha = 0.8) + 
  facet_grid(cat~resvar, labeller = label_parsed
    ) + 
  geom_vline(xintercept = 0, linetype = 'dashed') + 
  mythm + 
  xlab(expression(tau)) +
  scale_shape_manual(values = c(16, 1, 17, 2)) +
  scale_colour_gradient(low = 'grey60', high = 'black', guide = F) + 
  scale_x_continuous(limits = c(-1, 1)) + 
  geom_hline(yintercept = c(3.5, 6.5), colour = 'grey', alpha = 0.6) + 
  scale_y_discrete('Stations')

# seasonal, first years
toplo2 <- filter(trnds_seasyr, !cat %in% c('1976-1995', '1996-2013')& ann == 'bef') 
p2 <- ggplot(toplo2, aes(x = tau, y = Site_Code)) + 
  geom_point(aes(pch = trnd, colour = abs(tau)), size = 4, alpha = 0.8) + 
  facet_grid(cat~resvar, labeller = label_parsed
    ) + 
  geom_vline(xintercept = 0, linetype = 'dashed') + 
  mythm + 
  xlab(expression(tau)) +
  scale_shape_manual(values = c(16, 1, 17, 2)) +
  scale_colour_gradient(low = 'grey60', high = 'black', guide = F) + 
  scale_x_continuous(limits = c(-1, 1)) + 
  geom_hline(yintercept = c(3.5, 6.5), colour = 'grey', alpha = 0.6) + 
  scale_y_discrete('Stations')

# seasonal, first years
toplo3 <- filter(trnds_seasyr, !cat %in% c('1976-1995', '1996-2013')& ann == 'aft')
p3 <- ggplot(toplo3, aes(x = tau, y = Site_Code)) + 
  geom_point(aes(pch = trnd, colour = abs(tau)), size = 4, alpha = 0.8) + 
  facet_grid(cat~resvar, labeller = label_parsed
    ) + 
  geom_vline(xintercept = 0, linetype = 'dashed') + 
  mythm + 
  xlab(expression(tau)) +
  scale_shape_manual(values = c(16, 1, 17, 2)) +
  scale_colour_gradient(low = 'grey60', high = 'black', guide = F) + 
  scale_x_continuous(limits = c(-1, 1)) + 
  geom_hline(yintercept = c(3.5, 6.5), colour = 'grey', alpha = 0.6) + 
  scale_y_discrete('Stations')
